%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	content
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cvproject
    {\textbf{KECC - KAIST Educational C Compiler}}
    {Spring 2023}
    {
      \begin{cvitems}
          \item {Implemented a compiler that covers subset of C language for RISC-V architecture.}
          \item {Implemented optimizations such as Mem2Reg, GVN, Deadcode-elim}
          \item {Used Rust as implementation language}
      \end{cvitems}
    }
  \cvproject
    {\textbf{Arcade Transaction System}} % organization
    {Spring 2023} % date(s)
    {
      \begin{cvitems} % description(s) of tasks/responsibilities
        \item {Designed and implemented a system for running Arcades (managing games, tickets, prizes)}
        \item {Made frontend, backend, and a PC application for the System}
        \item {Used React for frontend, FastAPI for backend, and Electron for PC Application}
      \end{cvitems}
    }

  \cvproject
    {\textbf{Testing Setup Generation for Django projects}}
    {Spring 2023}
    {
      \begin{cvitems}
        \item {Implemented a static analyzer to extract entity information and API information from Django project}
        \item {Tool is able able to automatically generate sequence of API calls to test the REST API}
      \end{cvitems}
    }
  \cvproject
    {\textbf{Coverage Profiler for Python}}
    {Spring 2023}
    {
      \begin{cvitems}
          \item {Instrumented Python code to measure coverage.}
          \item {Tool is able to measure statement, branch, and condition coverage.}
      \end{cvitems}
    }
  \cvproject
    {\textbf{Mutation Testing Tool for Python}}
    {Spring 2023}
    {
      \begin{cvitems}
          \item {Implemented a number of mutation operators that mutate Python source code and produce diffs.}
          \item {Implemented complete mutation testing framework.}
      \end{cvitems}
    }
  \cvproject
    {\textbf{Analysis of Fake News Using Topic Modeling}}
    {Fall 2022} % date(s)
    {
      \begin{cvitems} % description(s) of tasks/responsibilities
        \item {Analysed big data in order to know if there's any relation between topics that fake/controversial and real news cover}
        \item {Used LDA to generate topics on news.}
        \item {Evaluated LDA models with coherence values.}
        \item {Used well-known Python libraries for data analysis and visualization.}
      \end{cvitems}
    }%---------------------------------------------------------
\end{cventries}